Using tours to visually investigate properties of new projection pursuit indexes with application to problems in physics

### 2018-11-02 scagnostics.Rmd
Structured labels fixed, data added.

FIXME yes/no labels appear to be inverted?

@@

getIdx <- function(dataT, size, structured){
  convex <- numeric(length = 100)
  skinny <- numeric(length = 100)
  stringy <- numeric(length = 100)
  micidx <- numeric(length = 100)
  ticidx <- numeric(length = 100)
  dcor2D <- numeric(length = 100)
  splines2D <- numeric(length = 100)
  for(i in 1:100){
    cSample <- getSample(dataT, size)
    if(structured){
      x = as.numeric(cSample$V1)
      y = as.numeric(cSample$V2)
    } else{
      x = as.numeric(cSample$V5)
      y = as.numeric(cSample$V6)
    }
    scag <- scagnostics(x=x, y=y)$s
    midx <- mine(x, y, est = "mic_e")
    skinny[i] <- scag["Skinny"]
    stringy[i] <- scag["Stringy"]
    convex[i] <- scag["Convex"]
    micidx[i] <- midx$MIC
    ticidx[i] <- midx$TIC
    dcor2D[i] <- dcor2d(x=x, y=y)
    splines2D[i] <- splines2d(x,y)
  }
  lapply(c(skinny, stringy, convex, micidx, ticidx, dcor2D, splines2D), sort)
  res <- tableTemp() %>%
    add_row(index="Skinny", data=dataT, size=size,
            structured=ifelse(structured, "yes", "no"),
            value5=skinny[5], value95=skinny[95]) %>%
    add_row(index="Stringy", data=dataT, size=size,
            structured=ifelse(structured, "yes", "no"),
            value5=stringy[5], value95=stringy[95]) %>%
    add_row(index="Convex", data=dataT, size=size,
            structured=ifelse(structured, "yes", "no"),
            value5=convex[5], value95=convex[95]) %>%
    add_row(index="MICe", data=dataT, size=size,
            structured=ifelse(structured, "yes", "no"),
            value5=micidx[5], value95=micidx[95]) %>%
    add_row(index="TICe", data=dataT, size=size,
            structured=ifelse(structured, "yes", "no"),
            value5=ticidx[5], value95=ticidx[95]) %>%
    add_row(index="dcor2D", data=dataT, size=size,
            structured=ifelse(structured, "yes", "no"),
            value5=dcor2D[5], value95=dcor2D[95]) %>%
    add_row(index="splines2D", data=dataT, size=size,
            structured=ifelse(structured, "yes", "no"),
            value5=splines2D[5], value95=splines2D[95])
}

>>>>

@@

getIdx <- function(dataT, size, structured){
  convex <- numeric(length = 100)
  skinny <- numeric(length = 100)
  stringy <- numeric(length = 100)
  micidx <- numeric(length = 100)
  ticidx <- numeric(length = 100)
  dcor2D <- numeric(length = 100)
  splines2D <- numeric(length = 100)
  for(i in 1:100){
    cSample <- getSample(dataT, size)
    if(!structured){
      x = as.numeric(cSample$V1)
      y = as.numeric(cSample$V2)
    } else{
      x = as.numeric(cSample$V5)
      y = as.numeric(cSample$V6)
    }
    scag <- scagnostics(x=x, y=y)$s
    midx <- mine(x, y, est = "mic_e")
    skinny[i] <- scag["Skinny"]
    stringy[i] <- scag["Stringy"]
    convex[i] <- scag["Convex"]
    micidx[i] <- midx$MIC
    ticidx[i] <- midx$TIC
    dcor2D[i] <- dcor2d(x=x, y=y)
    splines2D[i] <- splines2d(x,y)
  }
  lapply(c(skinny, stringy, convex, micidx, ticidx, dcor2D, splines2D), sort)
  res <- tableTemp() %>%
    add_row(index="Skinny", data=dataT, size=size,
            structured=ifelse(structured, "yes", "no"),
            value5=skinny[5], value95=skinny[95]) %>%
    add_row(index="Stringy", data=dataT, size=size,
            structured=ifelse(structured, "yes", "no"),
            value5=stringy[5], value95=stringy[95]) %>%
    add_row(index="Convex", data=dataT, size=size,
            structured=ifelse(structured, "yes", "no"),
            value5=convex[5], value95=convex[95]) %>%
    add_row(index="MICe", data=dataT, size=size,
            structured=ifelse(structured, "yes", "no"),
            value5=micidx[5], value95=micidx[95]) %>%
    add_row(index="TICe", data=dataT, size=size,
            structured=ifelse(structured, "yes", "no"),
            value5=ticidx[5], value95=ticidx[95]) %>%
    add_row(index="dcor2D", data=dataT, size=size,
            structured=ifelse(structured, "yes", "no"),
            value5=dcor2D[5], value95=dcor2D[95]) %>%
    add_row(index="splines2D", data=dataT, size=size,
            structured=ifelse(structured, "yes", "no"),
            value5=splines2D[5], value95=splines2D[95])
}
